---
title: "Masters project in ABC"
author: "Zee"
date: "6/20/2019"
output: html_document
---
#
#
#
#
#### Plot of the SIR model under which ABC simulations will be performed. From this model, we obtain six target features as follows : 
#
#
######## Incidence at time 25
######## Incidence at time 50
######## Incidence at time 75
######## Cummulative Incidence
######## Peak Incidence
######## Time at which Peak Incidence occurs
#
#
```{r, warning=FALSE,message=FALSE}
library(EasyABC)
library(deSolve)

sir <- function(t, x, parms)  {
  with(as.list(c(parms, x)), {
    N = S+I+R
    dS = -1 * beta * I/N * S
    dI = beta * I/N * S - gamma * I
    dR = gamma * I
    dCumInc = beta * I/N * S
    output <- c(dS, dI, dR, dCumInc)
    list(output)
  })
}
start<-c(S=990, I=10, R=0, CumInc=0) #the Initial values

times <- seq(0, 75, 1) # time period 
parms <- c(beta=runif(1,0,1), gamma= runif(1,0,0.5)) ## The parameters 

run<-ode(times=times, y=start, func=sir,parms=parms) # ode solver
Inc = c(0,diff(run[,5]))
model_res_inc = cbind(run,Inc) # adds incidence column to the results from te ode solver



plot(model_res_inc[,2],col="blue4", type="l",ylim=c(0,1000),main="plot of the SIR model"
     ,xlab="Time", ylab="model_ouputs") # S
lines(model_res_inc[,3], col="orange")#I
lines(model_res_inc[,4],col="green")#R
lines(model_res_inc[,5], col="purple")#CUMI
lines(model_res_inc[,6], col="red") #Inc

lines(model_res_inc[,2]+model_res_inc[,3]+model_res_inc[,4],col="brown")
legend("topleft", legend=c("S", "Prev", "R","CumInc", "Inc","Pop"),col=c("blue4","orange",
       "green","purple","red","brown"), pch = 19, cex = 0.65,bg=8 )


```


### Creating a function to be used in ABC methods

```{r}
modelABC <- function(parameters) {
sir <- function(t, x, parms)  {
  with(as.list(c(parms, x)), {
    N = S+I+R
    dS = -1 * beta * I/N * S
    dI = beta * I/N * S - gamma * I
    dR = gamma * I
    dCumInc = beta * I/N * S
    output <- c(dS, dI, dR, dCumInc)
    list(output)
  })
}
start<-c(S=990, I=10, R=0, CumInc=0) #the Initial values
# cummulative incidence at time 0 = 0 -> incidence at time 0 = 0

times <- seq(0, 75, 1) # time period 
parms <- c(beta= parameters[1], gamma= parameters[2]) ## The parameters 

model_result <-ode(times=times, y=start, func=sir,parms=parms) # ode solver
Incidence = c(0,diff(model_result[,5])) # diff(cummulative incidence)
model_res_inc = cbind(model_result,Incidence) # adds incidence column to the results from te ode solver

targ = numeric() # create empty vector called targ
targ[1] = model_res_inc[25,6] # incidence at time 25
targ[2] = model_res_inc[50,6]  # incidence at time 50
targ[3] = model_res_inc[75,6] # incidence at time 75
targ[4] = model_res_inc[75,5] # CumIncncmulatve incidence
targ[5] = max(model_res_inc[,6])  #  peak incidence
targ[6] = which.max(model_res_inc[,6]) - 1  # time at which peak prevalence occures
return(targ)
}

#modelABC(c( runif(1,0,1) ,runif(1,0,0.5))) # run model to obtain targets once


```


### Running model 1000 times to obtain targets and storing targets in a 1000x6 matrix

```{r}
#############################################################################
# run model several times and save targets in a matrix

set.seed(123)

### save the results from 10000 runs, take the means as the targets
save_targets= matrix(c(0,0,0,0,0,0),1000,6)
for(i in 1:1000){
  save_targets[i,]= modelABC(c( runif(1,0,1) ,runif(1,0,0.5)))
}


####################################################################
# mean of targets
 
targets = c(round(mean(save_targets[,1]),4), round(mean(save_targets[,2]),4),
            round(mean(save_targets[,3]),4), round(mean(save_targets[,4]),4),
            round(mean(save_targets[,5]),4),round(mean(save_targets[,6]),4))


```


### Histograms of saved targets

```{r}
######################################################################

par(mfrow=c(3,2))
hist(save_targets[,1], main="incidence at time 25")
hist(save_targets[,2], main="incidence at time 50")
hist(save_targets[,3],  main="incidence at time 75")
hist(save_targets[,4],  main="cummulative incidence")
hist(save_targets[,5],  main="peak incidence")
hist(save_targets[,6], main="time for peak incidence")

########################################################################

```

### Histograms of saved targets with breaks

```{r}

my.breaks1 <- pretty(range(save_targets[,1]),76)
my.breaks2 <- pretty(range(save_targets[,2]),76)
my.breaks3 <- pretty(range(save_targets[,3]),76)
my.breaks4 <- pretty(range(save_targets[,4]),76)
my.breaks5 <- pretty(range(save_targets[,5]),76)
my.breaks6 <- pretty(range(save_targets[,6]),76)


par(mfrow=c(3,2))
hist(save_targets[,1],  breaks= my.breaks1, main="incidence at time 25")
hist(save_targets[,2],  breaks= my.breaks2, main="incidence at time 50")
hist(save_targets[,3],  breaks= my.breaks3,  main="incidence at time 75")
hist(save_targets[,4],  breaks= my.breaks4, main="cummulative incidence")
hist(save_targets[,5], breaks= my.breaks5,  main="peak incidence")
hist(save_targets[,6], breaks= my.breaks6, main="time for peak incidence")

########################################################################

```

#### 